QPLIB: A Library of Quadratic Programming Instances

### 2016-07-27 QPLIB-3.tex
Gams instead of GAMS

\paragraph{First Instances Filter.} As already mentioned an important characteristic of an instances is its computational difficulty, i.e., the CPU time needed by a complete solver (cf.~\S \ref{sec:algo}) to solve the instance to global optimality. Accordingly, for each of the gathered instance we run the solvers in {\tt GAMS} (see Table \ref{}) able to solve it to global optimality. The number of solvers depends on the category of the instances under consideration. Then in order to reduce the number of instances we performed a first filter based on a relative measure of computational difficulty, i.e., we discarded all ``easy'' instances which are solved by at least 30\% of the complete solvers within a time limit of 30 seconds. Thanks to this first filter we obtained what we call the {\it filtered test bed}.

@@

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Instance Format}\label{subsec:format}
\framebox{TASK X : write }
In the call for instances no specific formats were imposed
%we did not impose a specific format
for the submissions.
%In this phase we also eliminated multiples copies of the same instance.
To evaluate the instances we decided, for practical reasons, to use GAMS as common platform for all the experiments involving commercial solvers.
For this reason, we decided to translate all instances into the \texttt{.gms} gams format.
 In a preliminary phase, all the instances received were divided according to their format and subsequently translated.
In Sect.
%~\ref{subsec:CP_convex}
the tools used
to translate an instance from a given format to the \texttt{.gms} format
%to translate an instance from and to a given format to the \texttt{.gms} format
are described more in detail.\\

>>>>

\paragraph{First Instances Filter.} As already mentioned an important characteristic of an instances is its computational difficulty, i.e., the CPU time needed by a complete solver (cf.~\S \ref{sec:algo}) to solve the instance to global optimality. Accordingly, for each of the gathered instance we run the solvers in {\tt Gams} (see Table \ref{}) able to solve it to global optimality. The number of solvers depends on the category of the instances under consideration. Then in order to reduce the number of instances we performed a first filter based on a relative measure of computational difficulty, i.e., we discarded all ``easy'' instances which are solved by at least 30\% of the complete solvers within a time limit of 30 seconds. Thanks to this first filter we obtained what we call the {\it filtered test bed}.

@@

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Instance Format}\label{subsec:format}
\framebox{TASK X : write }
In the call for instances no specific formats were imposed
%we did not impose a specific format
for the submissions.
%In this phase we also eliminated multiples copies of the same instance.
To evaluate the instances we decided, for practical reasons, to use Gams as common platform for all the experiments involving commercial solvers.
For this reason, we decided to translate all instances into the \texttt{.gms} Gams format.
 In a preliminary phase, all the instances received were divided according to their format and subsequently translated.
In Sect.
%~\ref{subsec:CP_convex}
the tools used
to translate an instance from a given format to the \texttt{.gms} format
%to translate an instance from and to a given format to the \texttt{.gms} format
are described more in detail.\\
